The \dealii{} Library, Version 9.3

### 2021-05-28 9.3/paper.tex
Go through the rest of the paper.

TODO

@@

Until now, \dealii has only supported local smoothing multigrid
algorithms~\citep{ClevengerHeisterKanschatKronbichler2019}; in local
smoothing algorithms, smoothers only act on the cells of a given refinement level,
skipping those parts of the mesh that are not adaptively refined to that level.
The current release now also has support for global coarsening~\citep{becker2000multigrid, sundar2012parallel} when
using continuous (\texttt{FE\_Q}, \texttt{FE\_SimplexP}) and
discontinuous (\texttt{FE\_DGQ}, \texttt{FE\_SimplexDGP})
elements. Global coarsening builds multigrid levels for the entire
domain, coarsening \textit{all} cells of a triangulation regardless of
how many times they have been refined. In addition, the framework now available in
\dealii{} in not only applicable to geometric coarsening, but can also
perform coarsening by reducing the polynomial degree ($p$-multigrid,
see~\cite{Fehn2020}), for example
to support $hp$-adaptive meshes.
%where it has been shown that one can
%efficiently precondition high-order spaces with lower-order finite
%element operators.
% MK: I do not think "precondition" is a precise enough description of p-multigrid
% because one still needs smoothing on the fine levels in addition to the
% "solve" at the coarser degree, a fact not transported by the mere
% 'precondition' term; rather than trying to discuss this in a more precise way,
% let us simply skip it as that is not central to the presentation here.
Finally, the implementation also supports transfer between continuous
and discontinuous elements as a further way to create multigrid levels.

@@

The transfer operators between two levels have been implemented in the new class \texttt{MGTwoLevel\allowbreak Transfer}, which can be set up via the functions \texttt{MGTwoLevel\allowbreak Transfer::\allowbreak reinit\_\allowbreak geometric\_\allowbreak transfer()} or \texttt{MGTwo\allowbreak LevelTransfer::\allowbreak reinit\_\allowbreak polynomial\_\allowbreak transfer()} for given
\texttt{DoFHandler} and \texttt{AffineConstraint} classes of two levels. The resulting transfer operators
can then be collected in a single
\texttt{MGTransfer\allowbreak GlobalCoarsening} object that can be used just as the previous workhorse \texttt{MGTransferMatrixFree} within the \texttt{Multigrid}
algorithm.
%Several common operations are encoded in utility
%functions in the \texttt{MGTransferGlobalCoarseningTools}
%namespace.
To facilitate the construction of matrix diagonals with matrix-free methods as well as a matrix representation of the coarse level matrix, new utility functions \texttt{create\_diagonal()} and \texttt{create\_matrix()} from
the \texttt{MatrixFreeTools} namespace have been added (see also Subsection~\ref{subsec:mf}).

@@

@@

The classes \texttt{FEEvaluation} and \texttt{FEFaceEvaluation} use template parameters for
the polynomial degree of the finite element $k$ and the number of the 1D quadrature points $q$
to generate near-optimal code for these operations.
For application codes that rely on operators of many different degrees (e.g., because
they use $p$-multigrid or $hp$-algorithms), creating all instantiations
can be overly complex and incur long compile times.

In the current release, specializations of these classes that do
not rely on the template parameters $k$ and $q$ (expressed in the code
with ``-1'' and ``0'') have been added. For example:
\begin{c++}
FEEvaluation<dim, -1, 0, n_components, Number, VectorizedArrayType>
  phi(range, dofhandler_index, quadrature_index, first_selected_component);
\end{c++}
These classes select at runtime -- for common low and medium
polynomial degree/quadrature combinations ($k\le 6$ and $q\in\{ k+1,
k+2, \left\lfloor (3k)/2 \right\rfloor \}$) -- efficient precompiled implementations and default to non-templated
evaluation kernels else.

@@

With release 9.1 \cite{dealII91}, large parts of the $hp$-algorithms in \dealii were parallelized, enabling
parallel matrix-based simulations with the $hp$-infrastructure. In the present
release, the parallel $hp$ support was extended to \texttt{MatrixFree}.

Until now, the \texttt{FEEvaluation} classes used the template parameters $k$ and $q$ to select the correct active FE and quadrature index and cumbersome detection of subranges of the same degree.
The creation of subranges is now performed internally, and the non-templated versions
of the \texttt{FEEvaluation} classes have been extended for the $hp$-case. To determine
the desired FE and quadrature index of a subrange, the current cell/face range has to be provided
to the constructors of the \texttt{FEEvaluation} classes. These changes enable
users to write matrix-free code independently of whether $hp$-capabilities are used or not.

@@

\subsection{MPI-3.0 shared-memory support}\label{subsec:sm}
In many large computations, certain pieces of data are computed once
and then treated as read-only. If this information is needed by more
than one MPI process, it is more efficient to store this information only
once in shared memory among all processes located on a multicore
node. MPI supports the creation of such shared memory windows since
version 3.0, and deal.II can now use this in the
\texttt{AlignedVector} and \texttt{Table} classes that are often used
for large lookup tables.

The feature is also used in the \texttt{MatrixFree} and
\texttt{LinearAlgebra::\allowbreak distributed::\allowbreak Vector} classes. If \texttt{MatrixFree} has been configured by setting
\texttt{MatrixFree::AdditionalData::communicator\_sm} appropriately, then
\texttt{MatrixFree::create\_dof\_vector()} creates vectors that share
information among all processes on one node. As a consequence, the
\texttt{FEEvaluation} classes can access vector elements owned by
other processes and in certain cases node-local
communication can be skipped. To prevent race conditions, \texttt{MatrixFree} uses local
barriers at the beginning and the end of loops (\texttt{loop()}, \texttt{cell\_loop()}, \texttt{loop\_cell\_centric()}).

@@

In a number of circumstances, finite element solutions need to be evaluated on
arbitrary reference points that change from one element to next. Two important
examples are particle simulations coupled to a finite element solution, or
algorithms on non-matching grids. The existing \texttt{FEValues} class is a poor
fit for this task, as it relies on tabulating all information before its usage,
necessitating a separate setup for every cell. The new class
\texttt{FEPointEvaluation} provides a more convenient interface for this
task. For tensor product finite elements (\texttt{FE\_Q}, \texttt{FE\_DGQ})
and tensor product mappings (\texttt{MappingQGeneric} and derived classes),
the new approach is also very fast, as it can use some of the matrix-free
infrastructure and vectorization facilities.

To give an example of the new features, let us consider the evaluation of a
surface tension force in the context of sharp-interface methods, whose
contribution is added to a fluid solver by multiplication with test function
and addition over quadrature points:
\begin{align*}
\left(\vec{v}, \kappa \, \vec{n}\right)_\Gamma
\approx
\sum_q\left(\vec{v}, \kappa(\vec{p}_q) \, \vec{n}(\vec{p}_q) (JxW)_q\right).
\end{align*}
In \dealii{}, this can now be conveniently written as
\begin{c++}
phi_normal.reinit(cell, reference_points);
phi_force.reinit(cell, reference_points);
phi_normal.evaluate(normal_values, EvaluationFlags::values);
for (unsigned int q = 0; q < n_points; ++q)
   phi_force.submit_value(phi_curvature.get_value(q) *
                          phi_normal.get_value(q) * JxW[q], q);
phi_force.integrate(force_values, EvaluationFlags::values);
\end{c++}
The quadrature points (at reference positions - \texttt{reference\_points}) and the related \texttt{JxW} value can, e.g., come from
a mesh of codimension one. Determining to which \texttt{cell} a quadrature
point belongs to on the background mesh, including the reference-cell
coordinates \texttt{reference\_points}, can be determined with functions like
\texttt{GridTools::find\_all\_active\_cells\_around\_point()}. While these
functions have been available in \dealii{} previously, their performance has
been considerably enhanced with the aforementioned more optimized code paths
for selected mappings.

While \texttt{FEPointEvaluation} assumes that evaluation points are already sorted according to 
the owning cells and such can concentrate on cell-local operations, the new class
\texttt{RemovePointEvaluation} is responsible to determine the owning cells in a distributed
context and for providing efficient communication patterns for the data exchange. In \texttt{deal.II},
the class has been successfully applied together with \texttt{FEPointEvaluation} to evaluate a distributed
solution vector at arbitrary points (see \texttt{VectorTools::evaluate\_at\_points()}).

@@

Many of the \dealii{} tutorial programs were revised in a variety of
ways as part of this release. TODO

In addition, there are a number of new tutorial programs:
\begin{itemize}
\item \texttt{step-19} is an introductory demonstration of \dealii{}'s
  particle functionality. It solves the coupled problem of
  charged particles and an electric field, using a cathode tube as an
  example.

\item \texttt{step-68} TODO

@@

\item \texttt{step-76} is an explicit time integrator for the
      compressible Euler equations discretized with a high-order discontinuous
      Galerkin (DG) scheme, using the matrix-free infrastructure just as \texttt{step-67} does.
      The tutorial presents advanced topics, like the usage of cell-centric loops and
      the new MPI-3.0 shared-memory capabilities of \texttt{MatrixFree} tor each high
      throughput. Furthermore, the utilization of the template parameter
      \texttt{VectorizedArrayType} and the application of lambdas to capture cell and face
      integrals are discussed.

\item \texttt{step-77} is a program that illustrate \texttt{dealii}'s
  interfaces to the SUNDIALS library \cite{sundials}, and specifically
  the KINSOL nonlinear solver. Like the \texttt{step-72} program
  mentioned above, it is a variation of the minimal surface solver
  \texttt{step-15}: Instead of implementing the nonlinear Newton and
  line search loop ourselves, \texttt{step-77} relies on KINSOL for
  decisions such as when to rebuild the Jacobian matrix, when to
  actually solve linear systems with it, and how to form updates that
  drive the residual to convergence. The program illustrates the
  substantial savings that can be obtained by not re-inventing the
  wheel but instead building on an existing and well-tuned software
  such as KINSOL.

  \dealii{}'s interfaces were also updated to the latest SUNDIALS release, 5.7.

\item \texttt{step-78} TODO

\item \texttt{step-79} TODO
\end{itemize}

There is also a new program in the code gallery (a collection of
user-contributed programs that often solve more complicated problems
than tutorial programs, and intended as starting points for further
research rather than as teaching tools):
\begin{itemize}
  \item preCICE: TODO
\end{itemize}

@@

The 9.3 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_2_0_and_9_3_0.html}
{around 45 incompatible changes}; see \cite{changes93}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions; and the majority change internal
interfaces that are not usually used in external
applications. That said, the following are worth mentioning since they
may have been more widely used:
\begin{itemize}
  \item The \texttt{hp::DoFHandler} class has been deprecated. The standard
        \texttt{DoFHandler} class is now capable of all $hp$-functionalities.
  \item Consequently, all template arguments \texttt{DoFHandlerType} are obsolete,
        and classes like \texttt{DataOut} or \texttt{SolutionTransfer} for example
        no longer require them. If you rely on these template arguments, an interim
        namespace \texttt{Legacy} has been introduced that provides all affected
        classes with the old interface for the transition phase.
\end{itemize}

@@

In order to justify the work the developers of \dealii{} put into this
software, we ask that papers using the library reference one of the
\dealii{} papers. This helps us justify the effort we put into it.

@@

The original \dealii{} paper containing an overview of its
architecture is \cite{BangerthHartmannKanschat2007}. If you rely on
specific features of the library, please consider citing any of the
following:
\begin{multicols}{2}
  \vspace*{-36pt}
  \begin{itemize}
    \item For geometric multigrid: \cite{Kanschat2004,JanssenKanschat2011,ClevengerHeisterKanschatKronbichler2019};
    \item For distributed parallel computing: \cite{BangerthBursteddeHeisterKronbichler11};
    \item For $hp$-adaptivity: \cite{BangerthKayserHerold2007};
    \item For partition-of-unity (PUM) and enrichment methods of the
          finite element space: \cite{Davydov2016};
    \item For matrix-free and fast assembly techniques:
          \cite{KronbichlerKormann2012,KronbichlerKormann2019};
    \item For computations on lower-dimensional manifolds:
          \cite{DeSimoneHeltaiManigrasso2009};
    \item For curved geometry representations and manifolds:
          \cite{HeltaiBangerthKronbichlerMola2019};
          \vfill\null  \columnbreak
    \item For integration with CAD files and tools:
          \cite{HeltaiMola2015};
    \item For boundary element computations:
          \cite{GiulianiMolaHeltai-2018-a};
    \item For \texttt{LinearOperator} and \texttt{PackagedOperation} facilities:
          \cite{MaierBardelloniHeltai-2016-a,MaierBardelloniHeltai-2016-b};
    \item For uses of the \texttt{WorkStream} interface:
          \cite{TKB16};
    \item For uses of the \texttt{ParameterAcceptor} concept, the
          \texttt{MeshWorker::ScratchData} base class, and the
          \texttt{ParsedConvergenceTable} class:
          \cite{SartoriGiulianiBardelloni-2018-a};
    \item For uses of the particle functionality in \dealii{}:
          \cite{GLHPB18}.
          \vfill\null
  \end{itemize}
\end{multicols}

@@

\dealii{} is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people
contributed code to this release:\\
%
% Uwe Koecher doesn't usually show up in the changelog, but
% we should make sure he's listed.
%
% 9.3: updated 5/08/2021 PM
Alexander Grayver,
Andrew Davis,
Arpit Babbar,
Bruno Blais,
Bruno Turcksin,
Ce Qin,
Christoph Kammer,
Conrad Clevenger,
Dominic Soldner,
Daniel Arndt,
Daniel Garcia-Sanchez,
Daniel Paukner,
David F. Castellanos,
David Wells,
Doug Shi-Dong,
David Schneider,
Elias Dejene,
Graham Harper,
Ignacio Tomas,
Ivan Fumagalli,
Jake Harmon,
Jean-Paul Pelteret,
Jiaqi Zhang,
Julian Roth,
Katharina Kormann,
Konrad Simon,
Krishnakumar Gopalakrishnan,
Laura Prieto Saavedra,
Lei Qiao,
Luca Heltai,
Magdalena Schreter,
Malhar Tidke,
Marc Fehling,
Marcus Calhoun-Lopez,
Martin Kronbichler ,
Mathias Anselmann,
Matthias Maier,
Maximilian Bergbauer,
Menno Fraters,
Michele Bucelli,
Nicola Giuliani,
Nicolas Barnafi,
Niklas Fehn,
Nils Much,
Olivier Guevremont,
Pasquale Africa,
Peter Munch,
Peter Westerbaan,
Phillip Mobley,
Pratik Nayak,
Praveen Chandrashekar,
Rene Gassmoeller,
Reza Rastak,
Richard Schussnig,
Sebastian Proell,
Simon Sticko,
Timo Heister,
Toni El Geitani Nehme,
Wenyu Lei,
Wolfgang Bangerth,
Zhou Lei

@@

W.~Bangerth, T.~C.~Clevenger, and T.~Heister were partially
supported by the Computational Infrastructure
in Geodynamics initiative (CIG), through the National Science
Foundation under Award No.~EAR-1550901 and The
University of California -- Davis.

@@

%D.~Davydov was supported by the German Research Foundation (DFG), grant DA
%1664/2-1 and the Bayerisches Kompetenznetzwerk
%f\"ur Technisch-Wissenschaftliches Hoch- und H\"ochstleistungsrechnen
%(KONWIHR).

B.~Blais was partially supported by the National Science and Engineering Research Council of Canada(NSERC)  through the RGPIN-2020-04510 Discovery Grant

T.~C.~Clevenger was also partially supported EAR-1925575 and OAC-2015848.

A.~V.~Grayver was partially supported by the European Space Agency
Swarm DISC program.

@@

Z.~Wang was partially
supported by the National Science Foundation under award OAC-1835673.

@@

The authors acknowledge the Texas Advanced Computing Center (TACC) at The
University of Texas at Austin for providing access to HPC resources that have
contributed to the research results reported within this paper.

Clemson University is acknowledged for generous allotment of compute time on
the Palmetto cluster.

>>>>

\todo[inline]{TODO}

@@

Until now, \dealii has only supported ``local smoothing'' multigrid
algorithms~\citep{ClevengerHeisterKanschatKronbichler2019} wherein
smoothers only act on the cells of a given refinement level,
skipping those parts of the mesh that have not been adaptively refined
to that level. This approach guarantees that the work done summed up
over all levels is proportional to the number of unknowns, and is
consequently necessary so that the overall multigrid preconditioner
can have a complexity of ${\cal O}(N)$.

In contrast, the current release now also supports ``global
coarsening'' algorithms \citep{becker2000multigrid, sundar2012parallel} when
using continuous (\texttt{FE\_Q}, \texttt{FE\_SimplexP}) and
discontinuous (\texttt{FE\_DGQ}, \texttt{FE\_SimplexDGP})
elements. Global coarsening builds multigrid levels for the entire
domain, coarsening \textit{all} cells of a triangulation regardless of
how many times they have been refined. In addition, the framework now available in
\dealii{} in not only applicable to geometric coarsening, but can also
perform coarsening by reducing the polynomial degree ($p$-multigrid,
see~\cite{Fehn2020}), for example
to support $hp$-adaptive meshes.
%where it has been shown that one can
%efficiently precondition high-order spaces with lower-order finite
%element operators.
% MK: I do not think "precondition" is a precise enough description of p-multigrid
% because one still needs smoothing on the fine levels in addition to the
% "solve" at the coarser degree, a fact not transported by the mere
% 'precondition' term; rather than trying to discuss this in a more precise way,
% let us simply skip it as that is not central to the presentation here.
Finally, the implementation also supports transfer between continuous
and discontinuous elements as a further way to create multigrid levels.

@@

The transfer operators between two levels have been implemented in the new class \texttt{MGTwoLevel\allowbreak Transfer}, which can be set up via the functions \texttt{MGTwoLevel\allowbreak Transfer::\allowbreak reinit\_\allowbreak geometric\_\allowbreak transfer()} or \texttt{MGTwo\allowbreak LevelTransfer::\allowbreak reinit\_\allowbreak polynomial\_\allowbreak transfer()} for given
\texttt{DoFHandler} and \texttt{AffineConstraint} objects
corresponding to the two levels. The resulting transfer operators
can then be collected in a single
\texttt{MGTransfer\allowbreak GlobalCoarsening} object that can be used just as the previous workhorse \texttt{MGTransferMatrixFree} within the \texttt{Multigrid}
algorithm.
%Several common operations are encoded in utility
%functions in the \texttt{MGTransferGlobalCoarseningTools}
%namespace.
To facilitate the construction of matrix diagonals with matrix-free methods as well as a matrix representation of the coarse level matrix, new utility functions \texttt{create\_diagonal()} and \texttt{create\_matrix()} from
the \texttt{MatrixFreeTools} namespace have been added (see also Subsection~\ref{subsec:mf}).

@@

\dealii{}'s matrix-free framework enables high-throughput operations
for applications in which only the availability of the \textit{action}
of a matrix, but not the entries of the matrix, are necessary. This
framework has been substantially extended in the current release.

@@

The \texttt{FEEvaluation} and \texttt{FEFaceEvaluation} classes use template parameters for
the polynomial degree of the finite element $k$ and the number of the 1D quadrature points $q$
to generate near-optimal code for these operations.
For application codes that rely on operators of many different degrees (e.g., because
they use $p$-multigrid or $hp$-algorithms), creating all instantiations
can be overly complex and incur long compile times.

In the current release, specializations of these classes that do
not rely on the template parameters $k$ and $q$ (expressed in the code
using special values ``-1'' and ``0'') have been added. For example:
\begin{c++}
FEEvaluation<dim, -1, 0, n_components, Number, VectorizedArrayType>
  phi(range, dofhandler_index, quadrature_index, first_selected_component);
\end{c++}
These classes select at runtime -- for common low and medium
polynomial degree/quadrature combinations ($k\le 6$ and $q\in\{ k+1,
k+2, \left\lfloor (3k)/2 \right\rfloor \}$) -- efficient precompiled implementations and default to non-templated
evaluation kernels else.

@@

With release 9.1, large parts of the $hp$-algorithms
in \dealii were ported to a model that allows for
parallel matrix-based simulations \cite{dealII91}. In the present
release, the parallel $hp$ support was extended to \texttt{MatrixFree}.

Until now, the \texttt{FEEvaluation} classes used the template
parameters $k$ and $q$ to select the correct active FE and quadrature
index and cumbersome detection of subranges of the same degree.
\todo{I don't understand what ``detection of subranges of the same
  degree'' refers to. Please clarify. In particular, I don't know what
``subranges'' mean in this paragraph.}
The creation of subranges is now performed internally, and the non-templated versions
of the \texttt{FEEvaluation} classes have been extended for the $hp$-case. To determine
the desired FE and quadrature index of a subrange, the current cell/face range has to be provided
to the constructors of the \texttt{FEEvaluation} classes. These changes enable
users to write matrix-free code independently of whether $hp$-capabilities are used or not.

@@

\subsection{MPI-3.0 shared-memory support}\label{subsec:sm}
In many large computations, certain pieces of data are computed
(or read from disk) once and then treated as read-only. If this information is needed by more
than one MPI process, it is more efficient to store this information only
once in shared memory among all processes located on a multicore
node. MPI supports the creation of such shared memory windows since
version 3.0, and deal.II can now use this in the
\texttt{AlignedVector} and \texttt{Table} classes that are often used
for large lookup tables for classes such as \texttt{InterpolatedTensorProductGridData}.

Shared memory storage is also used in the \texttt{MatrixFree} and
\texttt{LinearAlgebra::\allowbreak distributed::\allowbreak Vector} classes. If \texttt{MatrixFree} has been configured by setting
\texttt{MatrixFree::\allowbreak AdditionalData::\allowbreak communicator\_sm} appropriately, then
\texttt{MatrixFree::create\_dof\_vector()} creates vectors that share
information among all processes on one node. As a consequence, the
\texttt{FEEvaluation} classes can access vector elements owned by
other processes and in certain cases node-local
communication can be skipped. To prevent race conditions, \texttt{MatrixFree} uses local
barriers at the beginning and the end of loops (\texttt{loop()}, \texttt{cell\_loop()}, \texttt{loop\_cell\_centric()}).

@@

In a number of circumstances, finite element solutions need to be evaluated at
arbitrary reference points that change from one element to next. Two important
examples are particle simulations coupled to a finite element solution, or
algorithms on non-matching grids. The existing \texttt{FEValues} class is a poor
fit for this task, as it is based on the assumption that evaluation of
shape functions and their derivatives happens at the same quadrature
points on every cell, and that consequently expensive computations can
be done once and results re-used for many subsequent cells. The new class
\texttt{FEPointEvaluation} provides a more convenient interface for
cases where the evaluation on different cells does not happen at the
same points mapped from the reference cell.
For tensor product finite elements (\texttt{FE\_Q}, \texttt{FE\_DGQ})
and tensor product mappings (\texttt{MappingQGeneric} and derived classes),
the new approach is also very fast, as it can use some of the matrix-free
infrastructure and vectorization facilities.

To give an example of the new features, let us consider the evaluation of a
surface tension force in the context of sharp-interface methods, whose
contribution is added to a fluid solver by multiplication with test function
and addition over quadrature points located at the interface section
$\Gamma_K=\Gamma \cup K$ located on the current cell $K$ and that is,
in general, located differently within $K$ than for any other cell:
\begin{align*}
\left(\mathbf{v}, \kappa \, \mathbf{n}\right)_\Gamma
\approx
\sum_q \mathbf{v}(\mathbf{x}_q) \cdot \left(\kappa(\mathbf{x}_q) \, \mathbf{n}(\mathbf{x}_q)\right) (JxW)_q.
\end{align*}
In \dealii{}, this can now be conveniently written as
\begin{c++}
phi_normal.reinit(cell, reference_points);
phi_force.reinit(cell, reference_points);
phi_normal.evaluate(normal_values, EvaluationFlags::values);
for (unsigned int q = 0; q < n_points; ++q)
   phi_force.submit_value(phi_curvature.get_value(q) *
                          phi_normal.get_value(q) * JxW[q], q);
phi_force.integrate(force_values, EvaluationFlags::values);
\end{c++}
The quadrature points (at reference positions
\texttt{reference\_points}) and the related \texttt{JxW} value can,
for example, come from
a mesh of lower dimension. Determining to which \texttt{cell} a quadrature
point belongs to on the background mesh, including the reference cell
coordinates \texttt{reference\_points}, is aided by functions like
\texttt{GridTools::find\_all\_active\_cells\_around\_point()}. While these
functions have been available in \dealii{} previously, their performance has
been considerably enhanced with the aforementioned more optimized code paths
for selected mappings.

While \texttt{FEPointEvaluation} assumes that evaluation points are already sorted according to 
the owning cells and thus can focus on cell-local operations, the new class
\texttt{RemotePointEvaluation} is responsible for determine the owning cells in a distributed
context and for providing efficient communication patterns for the data exchange. In \texttt{deal.II},
the class has been successfully applied together with \texttt{FEPointEvaluation} to evaluate a distributed
solution vector at arbitrary points (see also the
\texttt{VectorTools::evaluate\_at\_points()} function).

@@

Many of the \dealii{} tutorial programs were revised in a variety of
ways as part of this release. In addition, there are a number of new tutorial programs:
\begin{itemize}
\item \texttt{step-19} is an introductory demonstration of \dealii{}'s
  particle functionality. It solves the coupled problem of
  charged particles and an electric field, using a cathode tube as an
  example.

\item \texttt{step-68} \todo[inline]{TODO}

@@

\item \texttt{step-76} is an explicit time integrator for the
      compressible Euler equations discretized with a high-order discontinuous
      Galerkin (DG) scheme, using the matrix-free infrastructure just as \texttt{step-67} does.
      The tutorial presents advanced topics, like the usage of cell-centric loops and
      the new MPI-3.0 shared-memory capabilities of \texttt{MatrixFree} to reach high
      throughput. Furthermore, the utilization of the template parameter
      \texttt{VectorizedArrayType} and the application of lambda functions to describe cell and face
      integrals are discussed.

\item \texttt{step-77} is a program that illustrate \dealii{}'s
  interfaces to the SUNDIALS library \cite{sundials}, and specifically
  the KINSOL nonlinear solver. Like the \texttt{step-72} program
  mentioned above, it is a variation of the minimal surface solver
  \texttt{step-15}: Instead of implementing the nonlinear Newton and
  line search loop ourselves, \texttt{step-77} relies on KINSOL for
  decisions such as when to rebuild the Jacobian matrix, when to
  actually solve linear systems with it, and how to form updates that
  drive the residual to convergence. The program illustrates the
  substantial savings that can be obtained by not re-inventing the
  wheel but instead building on an existing and well-tuned software
  such as KINSOL.

  \dealii{}'s interfaces to the various SUNDIALS sub-packages were also updated to the latest SUNDIALS release, 5.7.

\item \texttt{step-78} \todo[inline]{TODO}

\item \texttt{step-79} \todo[inline]{TODO}
\end{itemize}

There is also a new program in the code gallery (a collection of
user-contributed programs that often solve more complicated problems
than tutorial programs, and intended as starting points for further
research rather than as teaching tools):
\begin{itemize}
  \item preCICE: \todo[inline]{TODO}
\end{itemize}

@@

The 9.3 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_2_0_and_9_3_0.html}
{around 45 incompatible changes}; see \cite{changes93}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions; and the majority change internal
interfaces that are not usually used in external
applications. That said, the following are worth mentioning since they
may have been more widely used:
\begin{itemize}
  \item The \texttt{hp::DoFHandler} class has been deprecated. The standard
        \texttt{DoFHandler} class is now capable of all $hp$-functionalities.
  \item Consequently, all template arguments \texttt{DoFHandlerType} are obsolete,
        and classes like \texttt{DataOut} or \texttt{SolutionTransfer} for example
        no longer require them. If you rely on these template arguments, an interim
        namespace \texttt{Legacy} has been introduced that provides all affected
        classes with the old interface for a transition period.
\end{itemize}

\todo[inline]{Check whether there are other things worth listing.}

@@

In order to justify the work the developers of \dealii{} put into this
software, we ask that papers using the library reference one of the
\dealii{} papers. This helps us justify the effort we put into this library.

@@

The original \dealii{} paper containing an overview of its
architecture is \cite{BangerthHartmannKanschat2007}, and a more recent
publication documenting \dealii{}'s design decisions is available as \cite{dealII2020design}. If you rely on
specific features of the library, please consider citing any of the
following:
\begin{multicols}{2}
  \vspace*{-36pt}
  \begin{itemize}
    \item For geometric multigrid: \cite{Kanschat2004,JanssenKanschat2011,ClevengerHeisterKanschatKronbichler2019};
    \item For distributed parallel computing: \cite{BangerthBursteddeHeisterKronbichler11};
    \item For $hp$-adaptivity: \cite{BangerthKayserHerold2007};
    \item For partition-of-unity (PUM) and finite element enrichment methods:
           \cite{Davydov2016};
    \item For matrix-free and fast assembly techniques:
          \cite{KronbichlerKormann2012,KronbichlerKormann2019};
    \item For computations on lower-dimensional manifolds:
          \cite{DeSimoneHeltaiManigrasso2009};
    \item For curved geometry representations and manifolds:
          \cite{HeltaiBangerthKronbichlerMola2019};
    \item For integration with CAD files and tools:
          \cite{HeltaiMola2015};
    \item For boundary element computations:
          \cite{GiulianiMolaHeltai-2018-a};
    \item For the \texttt{LinearOperator} and
      \texttt{Packaged\-Operation} facilities:
          \cite{MaierBardelloniHeltai-2016-a,MaierBardelloniHeltai-2016-b};
    \item For uses of the \texttt{WorkStream} interface:
          \cite{TKB16};
    \item For uses of the \texttt{ParameterAcceptor} concept, the
          \texttt{MeshWorker::ScratchData} base class, and the
          \texttt{ParsedConvergenceTable} class:
          \cite{SartoriGiulianiBardelloni-2018-a};
    \item For uses of the particle functionality in \dealii{}:
          \cite{GLHPB18}.
          \vfill\null
  \end{itemize}
\end{multicols}

@@

\dealii{} is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people
contributed code to this release:\\
%
% Uwe Koecher doesn't usually show up in the changelog, but
% we should make sure he's listed.
%
% 9.3: updated 5/08/2021 PM
%      sorted by WB 5/28
Pasquale Africa,
Tyler Anderson,
Mathias Anselmann,
Arpit Babbar,
Maximilian Bergbauer,
Nicolas Barnafi,
Bruno Blais,
Michele Bucelli,
Marcus Calhoun-Lopez,
Praveen Chandrashekar,
Conrad Clevenger,
David F. Castellanos,
Andrew Davis,
Elias Dejene,
Niklas Fehn,
Menno Fraters,
Ivan Fumagalli,
Daniel Garcia-Sanchez,
Rene Gassmoeller,
Nicola Giuliani,
Krishnakumar Gopalakrishnan,
Alexander Grayver,
Olivier Guevremont,
Jake Harmon,
Graham Harper,
Uwe K\"ocher,
Katharina Kormann,
Christoph Kammer,
Wenyu Lei,
Zhou Lei,
Phillip Mobley,
Nils Much,
Pratik Nayak,
Toni El Geitani Nehme,
Justin O'Connor,
Daniel Paukner,
Sebastian Proell,
Lei Qiao,
Ce Qin,
Reza Rastak,
Julian Roth,
Laura Prieto Saavedra,
Doug Shi-Dong,
David Schneider,
Magdalena Schreter,
Richard Schussnig,
Konrad Simon,
Dominic Soldner,
Simon Sticko,
Malhar Tidke,
Ignacio Tomas,
Peter Westerbaan,
Jiaqi Zhang.

\todo[inline]{Remove everyone who may end up being a co-author.}

@@

W.~Bangerth and T.~Heister were partially
supported by the Computational Infrastructure
in Geodynamics initiative (CIG), through the National Science
Foundation under Award No.~EAR-1550901 and The
University of California -- Davis.

@@

@@

@@

\todo[inline]{Everyone update. Add support for any additional authors.}
